---
title: "Report"
author: "JMS"
date: "`r as.character(Sys.Date())`"
output: 
  word_document:
    toc: true
    toc_depth: 4
    number_sections: true
    pandoc_args: ['-F', 'zotref.py', '--citeproc']
  html_document:
   pandoc_args: ['-F', 'zotref.py', '--citeproc']
params:
  format_out: "html"
  children: true
  message: true
  warning: true
bibliography: zotcite.bib
---

```{r settings, include=FALSE}
source("utils/setup.R")
options(knitr.table.format = ifelse(params$format_out == "html", "html", "simple"))
knitr::opts_knit$set(root.dir = rprojroot::find_root_file(criterion = ".git/index"))
```

# Aim
The aim of the study


# Children

If you want to include child documents, set `params$children` to `true` in the YAML header.
Calling chunk must be empty.

```{r child="children/child1.rmd", include=params$children}
```

## Data

Should be stored in `data/` folder. List the files below.

```{r data}
list.files("data")
```

## Population

The population is based on barn and not on graviditet (if i understand it correctly)

## Create variables


# References
If you want to include references. Requires zotref to be installed (from `nvim-R` or `zocite.nvim`)
<div id="refs"></div>


